---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data <- read.csv("./repdata_data_activity/activity.csv")
data <- transform(data,
                  interval=as.character(formatC(interval,width=4,flag = "0")))
```
## What is mean total number of steps taken per day?
```{r}
step_per_day <- as.data.frame(tapply(data$steps,data$date,sum))
  colnames(step_per_day)<-c("total_steps")
  hist(tapply(data$steps,data$date,sum),xlab = "steps per day",ylab = "",main = "")
  
  step_mean <- mean(step_per_day$total_steps, na.rm = TRUE)
  step_median <-median(step_per_day$total_steps, na.rm = TRUE)
  
  print(paste("mean:",step_mean))
  print(paste("median:",step_median))
```

## What is the average daily activity pattern?

steps increase in AM, decrease in PM, and few in midnight 

```{r}
steps_per_interval <- tapply(data$steps, data$interval, mean,na.rm=TRUE)
  
  steps_per_interval_df <-data.frame(
    interval=names(steps_per_interval),
    mean_steps=steps_per_interval)
  
    plot(steps_per_interval_df$interval,steps_per_interval_df$mean_steps,type="l",
         xlab = "intarval",ylab = "mean of steps per interval",main="")
```



## Imputing missing values

count NAs:
```{r}
print(paste("NA's:",sum(is.na(data))))
```

NAs replace zero.
```{r}
data2 <- data
data2[is.na(data2$steps),]<-0
step_per_day2 <- as.data.frame(tapply(data2$steps,data2$date,sum))
colnames(step_per_day2)<-c("total_steps")
hist(tapply(data2$steps,data2$date,sum),xlab = "steps per day",ylab = "",main = "")
  
step_mean2 <- mean(step_per_day2$total_steps)
step_median2 <-median(step_per_day2$total_steps)

print(paste("mean:",step_mean2))
print(paste("median:",step_median2))

```
Replacement from NA to zero makes difference value of mean and median. 

## Are there differences in activity patterns between weekdays and weekends?

```{r}
data3 <- transform(data,
  date=as.Date(date),
  interval=as.character(formatC(interval,width=4,flag = "0")))

day_of_week <- data.frame(weekdays(data3$date))

data3 <- cbind(data3,day_of_week)  

weekday <- data.frame(weekday="")

data3<- cbind(data3,weekday)

for (j in 1:nrow(data3)){
  if (data3$weekdays.data3.date.[j] %in% c("月曜日","火曜日","水曜日","木曜日","金曜日")){
    data3$weekday[j] <- "weekday"
    }else{
      data3$weekday[j] <- "weekend"
      }
  }
library(dplyr)
library(ggplot2)
data3.subset1 <- data3 %>% filter(weekday == "weekday")
data3.subset2 <- data3 %>% filter(weekday == "weekend")

weekday_mean_step <- tapply(data3.subset1$steps,data3.subset1$interval,mean,na.rm = TRUE)
weekend_mean_step <- tapply(data3.subset2$steps,data3.subset2$interval,mean,na.rm = TRUE)

weekday_mean_step_df <-data.frame(interval=names(weekday_mean_step),
                                  mean_step=weekday_mean_step,
                                  day="weekday")
weekend_mean_step_df <-data.frame(interval=names(weekend_mean_step),
                                  mean_step=weekend_mean_step,
                                  day="weekend")

data_weekdays <- rbind(weekday_mean_step_df,weekend_mean_step_df)

g <- ggplot(data=data_weekdays)
g <- g + facet_wrap(~day,nrow=2,ncol=1)
g <- g + geom_line(aes(x=interval,y=mean_step,group=day))

g


```
Weekend interval steps average more than daytime weekdays.
